---
title: "Forecasting time-varying transmission during the COVID-19 outbreak"
output:
  html_document:
    theme: cosmo
  pdf_document: default
---


```{r setup, include=FALSE}
#knitr::opts_knit$set(root.dir = 'epipredictr/')
#knitr::opts_knit$set(fig.path = 'inst/report/figure/')
```

```{r load-packages, include=FALSE}
library(epipredictr)
library(rstan)
options(mc.cores = 4)
rstan_options(auto_write = TRUE)
library(scoringutils)
library(dplyr)
library(cowplot)
# source("./R/utilities.R")
# source("./R/models.R")
```
#### Authors

# Summary
## Aim
Forecast the time-varying R_t estimates into the future to get a sense of the trajectory of the COVID-19 epidemic in different countries. 

## Abstract

## Methods
We used three different models

	1. windowed regression
	2. BSTS with a global trend
	3. BSTS with a local trend

to forecast transmission rates. Predictions were made using R and Stan and results were scored using CRPS and LogS using the scoringRules package. 

## Key Results

	[ ] graph with predictions by every country for best model
	[ ] table with 
		- CI for forecasts
		- Past forecast score? 



# Details



```{r load-data, echo = FALSE, results="hide"}
d <- readRDS("./data/time_varying_params.rds")[[1]]
y_true <- d$mean

```




```{r echo = FALSE, results="hide", message = FALSE, warning = FALSE}
## Windowed Regression 
# model_lin_reg <- stan_model(file = "./inst/stan/linear_regression.stan")
# res_lin <- fit_iteratively(incidences = y_true, model = model_lin_reg, 
# 						   n_pred = 7, 
#  					       max_n_past_obs = 7, vb = FALSE)

res_lin <- fit_iteratively(incidences = y_true, model = "lin_reg", n_pred = 7,	   				     max_n_past_obs = 7, vb = FALSE)



## BSTS global trend
# model_bsts <- stan_model(file = "./inst/stan/bsts.stan")
# res_bsts <- fit_iteratively(incidences = y_true, 
# 							model = model_bsts, n_pred = 7, 
# 							max_n_past_obs = Inf, vb = FALSE)
res_bsts <- fit_iteratively(incidences = y_true, 
							model = "bsts", n_pred = 7, 
							max_n_past_obs = Inf, vb = FALSE)



## BSTS local trend
# model_bsts_local <- stan_model(file = "./inst/stan/bsts_local_trend.stan")
# res_bsts_local <- fit_iteratively(incidences = y_true, 
# 								  model = model_bsts_local, 
# 								  n_pred = 7, 
# 								  max_n_past_obs = Inf, vb = FALSE)

res_bsts_local <- fit_iteratively(incidences = y_true, 
							model = "bsts_local_trend", n_pred = 7, 
							max_n_past_obs = Inf, vb = FALSE, 
							length_local_trend = 7)



```

## Model Fit

### Prior vs. Posterior Distributions

#### BSTS model global trend
```{r echo = FALSE, warning = FALSE}
prior_post <- plot_prior_vs_posterior(res_bsts$stanfitobjects)
prior_post$plot
```

#### BSTS model local trend
```{r echo = FALSE, warning = FALSE}
prior_post <- plot_prior_vs_posterior(res_bsts_local$stanfitobjects)
prior_post$plot
```

## Forecasts

### Table with forecasts

### Plots


```{r echo = FALSE, warning = FALSE}
p_reg <- plot_pred_vs_true(y_pred_samples = res_lin$predictive_samples, 
						y_true = res_lin$y, 
						forecast_run = res_lin$forecast_run)


p_bsts <- plot_pred_vs_true(y_pred_samples = res_bsts$predictive_samples, 
						y_true = res_bsts$y, 
						forecast_run = res_bsts$forecast_run)

p_bsts_local <- plot_pred_vs_true(y_pred_samples = res_bsts_local$predictive_samples, 
						y_true = res_bsts_local$y, 
						forecast_run = res_bsts_local$forecast_run)


plot_grid(p_reg, p_bsts, p_bsts_local, labels = "AUTO", ncol = 1)
```

## Scoring of Forecasts
```{r echo = FALSE}
scoringutils::eval_forecasts(true_values = y_true[15:76], 
							 predictions = res_lin$predictive_samples[15:76, ], 
							 outcome_type = "continuous")

scoringutils::eval_forecasts(true_values = y_true[15:76], 
							 predictions = res_bsts$predictive_samples[15:76, ], 
							 outcome_type = "continuous")

scoringutils::eval_forecasts(true_values = y_true[15:76], 
							 predictions = res_bsts_local$predictive_samples[15:76, ], 
							 outcome_type = "continuous")

```



