---
title: "Forecasting time-varying transmission during the COVID-19 outbreak"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{prediction_report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

*N. Bosse (1), S. Abbott (1), J. D. Munday (1), J. Hellewell (1), CMMID COVID team (1), S. Funk (1).*

*Correspondence to: nikos.bosse@lshtm.ac.uk* 

*1. Center for the Mathematical Modelling of Infectious Diseases, London School of Hygiene & Tropical Medicine, London WC1E 7HT, United Kingdom*

*Last Updated:* `r (Sys.Date() - 1)`

*Note: this is preliminary analysis, has not yet been peer-reviewed and is updated daily as new data becomes available. This work is licensed under a [Creative Commons Attribution 4.0 International License](https://creativecommons.org/licenses/by/4.0/). A summary of this report can be downloaded [here](https://cmmid.github.io/topics/covid19/current-patterns-transmission/reports/global-time-varying-transmission/summary.pdf)*




```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  echo = FALSE, eval = TRUE,
  #fig.width = 6, fig.height = 3,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  dpi = 320,
  fig.path = "figure/"
)
```

```{r load-packages, include=FALSE}
# library(epipredictr)
# library(rstan)
# options(mc.cores = 4)
# rstan_options(auto_write = TRUE)
library(ggplot2)
library(scoringutils)
library(dplyr)
library(cowplot)
library(patchwork)
library(bsts)
par(family = "Serif")
source("../R/utilities.R")
source("../R/forecast.R")
```


```{r load-data, include=FALSE}

inputdata <- load_all_timeseries(base_dir = "../data/results", date = as.Date("2020-03-09"))
inputdata <- inputdata[1:17, ]
incidences <- load_all_timeseries(base_dir = "../data/results", 
                                  date = as.Date("2020-03-09"), 
                                  ts_type = "incidences")



```

```{r do-analysis, include=FALSE}

models <- c("local", "semilocal", "local_student", "ar1", "ar2")
data <- list(inputdata = inputdata, 
			 last_date = max(inputdata$date),
             models = models,
             incidences = incidences,
             n_pred = 7,
             start_period = 4)

# analysis <- full_analysis(data)
# full_predictive_samples <- analysis$full_predictive_samples
# 
# all_scores <- scoring(data, analysis$full_predictive_samples)
# 
# aggregated_scores <- aggregate_scores(all_scores)
# 
# 
# 
# plot_scoring <- plot_scoring(data, aggregated_scores)




# predict_incidences <- predict_incidences(data, full_predictive_samples)


# 
# prediction_results <- lapply(
#   seq_along(analysis$countries),
#   FUN = function(i) {
#     region <- analysis$countries[i]
#     results_region_model <-
#       analysis$all_region_results[[region]]$region_results$average
#     forecast_table(results_region_model, region)
#   }
# )
# 
# summary_prediction_result <- do.call(rbind, prediction_results)

```


# Summary

### Aim
Forecast the time-varying $R_t$ estimates into the future to get a sense of the trajectory of the COVID-19 epidemic in different countries. 

### Abstract
some abstract.

## Key Results {.tabset}
### graph
Here will be a graph with predictions made by the best model
```{r Summary-results-graph}
# patchwork::wrap_plots(analysis$predictions_best, ncol = 2)

```

### table
Here will be a table that summarises predictions made by the best model
```{r Summary-results}
# knitr::kable(summary_prediction_result[,-1])
```

## Methods  {.tabset}

### Summary
- We used different Bayesian Structural Time Series Models from the R package bsts to forecast transmission rates ($R_0$). 
- Transmission rates were obtained according to https://cmmid.github.io/topics/covid19/current-patterns-transmission/global-time-varying-transmission.html. 

- The following Bayesian Structural Time Series Models were used: 

   1. BSTS with a local trend
   2. BSTS with a global trend
   3. BSTS with a local trend and a Student's-t-distribution 
   4. BSTS with an AR 1
   5. BSTS with an AR 2

- Results were assessed for calibration, bias, and sharpness and scored using the proper scoring rules CRPS and LogS with the scoringRules package.

### Limitations

#### $R_t$-estimates
- All limitations for estimating $R_t$ apply, especially: 

#### others
- time horizon
- linear trends --> would be good to have sth quadratic or sth following the derivative


### Detail

#### **Obtaining Estimates for $R_0$**
see https://cmmid.github.io/topics/covid19/current-patterns-transmission/global-time-varying-transmission.html
We obtain a time series with the median of estimated $R_t$ values. This time series is used for predictions. 

#### **Predicitions**
The time series is then forecasted into the future using the R package bsts. Forecasts are made every day for up to 7 days ahead. This allows us to validate the predictions against actual observations when they come in. For every time point we have multiple predictive samples, each based on different data x days ago, where x corresponds to the number of days forecasted into the future. The following models were used: 



##### BSTS with a local linear trend

The time series is modeled as 
$$\mu_t+1 = \mu+t + \delta_t + \epsilon_t, \quad \epsilon_t \sim \mathcal{N}(0, \sigma_{\mu}), $$
$$\delta_t = \delta_t + \eta_t, \quad \eta_t \sim \mathcal{N}(0, \sigma_{\delta}). $$
The local linear trend model therefore assumes that both the mean of the time series as well as the slope follow random walks. 

***
##### BSTS with a local linear trend and Student's-t-distributed errors
The model specification is very similar to the local linear trend model. The only change is that random errors now follow a t-distribution, which implies thicker tails and therefore more room for extreme changes. 
$$\mu_t+1 = \mu+t + \delta_t + \epsilon_t, \quad \epsilon_t \sim \mathcal{T}_{\nu_{\mu}}(0, \sigma_{\mu}), $$
$$\delta_{t+1} = \delta_t + \eta_t, \quad \eta_t \sim \mathcal{T}_{\nu_{\delta}}(0, \sigma_{\delta}). $$
$\nu_{\mu}$ and $\nu_{\delta}$ are parameters that determine the thickness of the tails. 

***
##### BSTS with a semi-local linear trend
The semi-local linear trend model assumes that the mean of the time series moves according to a random walk with slope. The slope component is an AR1 process centred on a constant trend D. For any non-zero value $\phi$, the slope will eventually become a constant number for long time horizons, resulting in a linear trend for the overall time series. Values of $\phi$ closer to one imply that the time series (or forecasts made by the model, respectively) will converge quicker to a purely linear trend. 
The time series is modeled as
$$\mu_t+1 = \mu+t + \delta_t + \epsilon_t, \quad \epsilon_t \sim \mathcal{N}(0, \sigma_{\mu}), $$
$$\delta_{t+1} = D + \phi (\delta_t -D), \quad \eta_t \sim \mathcal{N}(0, \sigma_{\delta}). $$


Maybe: plots for different trend values we made earlier. 

***
##### BSTS with an AR1 and AR2 state component
The mean of the time series is modeled as an AR(1)-process (or AR(2), respectively). The AR(1) model looks like this:

$$\alpha_t = \phi_1 \alpha_{t-1} + \epsilon_{t-1}, \quad \epsilon_t \sim \mathcal{N}(0, \sigma_{\delta}). $$
The AR(2) model looks like this:
$$\alpha_t = \phi_1 \alpha_{t-1} + \phi_2 \alpha_{t-2} + \epsilon_{t-1}, \quad \epsilon_t \sim \mathcal{N}(0, \sigma_{\delta}). $$
***
##### Model stacking
yet to be implemented


#### **Scoring**


##### PIT and calibration

##### bias

##### sharpness

##### CRPS

##### DSS


# Scoring {.tabset}

## Performance of 7-days-ahead-forecasts

## Performance across different forecasting horizons {.tabset}

### Calibration / PIT

### Bias

### Sharpness

### CRPS 

```{r Scoring-boxplot-different-horizons}

# plot_scoring$score_days_ahead

## maybe split in boxplot and lineplot

```

### DSS


## Scoring Tables {.tabset}

### Aggregated scores



### All scores
```{r Scoring-total-scores}
knitr::kable(analysis$scoring$across_country_scores)
```




# Detailed Results by country {.tabset}

## Japan {.tabset}

### Prediction vs. Actual

```{r Japan, fig.width=10, fig.height=18}
analysis$country_results$Japan$forecast_plot

```

### Prediction Scores
